Remark on the hypothetical judgment

### 2018-01-04 paper.tex
...

Now, in contrast to the treatment of the quantifiers in formal intuitionistic
logic (or in the Mitchell-B\'enabou language of a topos
\cite{maclane-moerdijk}), in this setting it is part of their meaning that their
verifications should respect the equality of the domain of discourse; this
constraint is called functionality, and reflects the fact that universal
quantification is reconstructed as a more general form of implication. Within
the theory of sets, there is simply not a quantifier which expresses
non-functional generality; in this way, contrary to the state of affairs in
\BISH{} \cite{bishop:1967}, the theorem of choice is in fact verified by a
choice \emph{function}, not merely a choice \emph{operation}.

>>>>

Now, in contrast to the treatment of the quantifiers in topos
logic~\cite{maclane-moerdijk}, in this setting it is part of their meaning that
their verifications should respect the equality of the domain of discourse;
this constraint is called functionality, and reflects the fact that universal
quantification is reconstructed as a more general form of implication. Within
the theory of sets, there is simply not a quantifier which expresses
non-functional generality; in this way, contrary to the state of affairs in
\BISH{} \cite{bishop:1967}, the theorem of choice is in fact verified by a
choice \emph{function}, not merely a choice \emph{operation}.
